---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# remav2

<!-- badges: start -->
[![R-CMD-check](https://github.com/AustralianAntarcticDivision/remav2/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/AustralianAntarcticDivision/remav2/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of remav2 is to provide access to the The Reference Elevation Model of Antarctica (REMA) v2 via its mosaic index. The index has been augmented to included geographic extent (xmin, xmax, ymin, ymax) and the actual GeoTIFF urls needed to read and interrogate the actual data with minimal fuss and plumbing.


## Installation

You can install the development version of remav2 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AustralianAntarcticDivision/remav2")
```

## Example

This is a basic example. 

Everything we need is in this index table. 

```{r example}
library(remav2)
library(dplyr)
(index <- remav2_index())
```


We can visualize the coverage of the tiles with their extents. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 9, fig.height = 9
)
```


```{r extent}
xlim <- range(unlist(index[c("xmin", "xmax")]))
ylim <- range(unlist(index[c("ymin", "ymax")]))
plot(NA, xlim = xlim, ylim = ylim, xlab = "x", ylab = "x", asp = 1)
rect(index$xmin, index$ymin, index$xmax, index$ymax)
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7, fig.height = 7
)
```

REMA v2 is an intensely detailed product, each of these tiles represents a raster grid with dimensions 25100x25100, with resolution of 2m. 

We can interrogate a specific place by finding the tile of interest. 


```{r tile}
## Casey station
pt <- cbind(2447000, -916300)
library(dplyr)
tile0 <- index |> filter(xmin <= pt[1], xmax >= pt[1], 
                         ymin <= pt[2], ymax >= pt[2])
tile0 |> dplyr::transmute(tile, data_percent, tif =  basename(cog_dem), xmin, xmax, ymin, ymax)
```


Now get an image from the browse file. 

```{r browse}
#devtools::install_github(c("hypertidy/whatarelief", "hypertidy/ximage"))
library(whatarelief)
library(ximage)
ex0 <- unlist(tile0[c("xmin", "xmax", "ymin", "ymax")])
im <- imagery(source = tile0$cog_browse, extent = ex0, dimension = c(1024, 1024), projection = "EPSG:3031")
ximage(im, extent = ex0, asp = 1)
```

Ah but ... how do we choose that 'pt' location in Polar Stereographic on the south pole with true scale latitude 72S oriented to longitude 0 (aka 'EPSG:3031')? 

Well, it's Casey station- we googled its longlat, and converted to 'EPSG:3031'. 

```{r project}
reproj::reproj_xy(cbind(110.5285, -66.2821), "EPSG:3031", source = "OGC:CRS84")

```

With that in mind, let's go for another location and get data for a broader region. 




```{r law-dome}
ld <-   cbind(112.826, -66.643)
pt <- reproj::reproj_xy(ld, "EPSG:3031", source = "OGC:CRS84")
ex <- c(-1, 1, -1, 1) * 1e5 + rep(pt, each = 2)
## we can do *this*, but it takes too long
#dsm <- imagery(source = index$cog_dem, extent = ex, dimension = c(1024, 1024), projection = "EPSG:3031")
tile1 <- index |> dplyr::filter(pmax(xmin, xmax) > ex[1], 
                       pmin(xmin, xmax) < ex[2], 
                       pmax(ymin, ymax) > ex[3], 
                       pmin(ymin, ymax) < ex[4] 
                       )

dim(tile1)
dsm <- elevation(source = tile1$cog_dem, extent = ex, dimension = c(1024, 1024), projection = "EPSG:3031")
ximage(dsm, extent = ex, asp = 1)

```

Of course, like other massive raster data sets this one is tiled and has overviews only within each tile so we can't efficiently treat it like a single data set, it's better for larger regions to go for the prepared lower resolution sources (a WIP for us to combine these levels). 

## WIP

TODO

- [ ] index the other resolutions
- [ ] integrate with a spatial helper package

## Code of Conduct
  
Please note that the remav2 project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
